Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2020-12-07 ms.tex
Adding x_init=6, 12 plots and filling out description paragraph of Monte Carlo and figures

\begin{figure}
    \centering
    \includegraphics{pdf_xinit0.0.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, results in an overall smaller fractional deviation from the Monte Carlo and a much closer match to the Monte Carlo in the wing.}
    \label{fig:sol_mc_residual}
\end{figure}

% Discussion of various solutions compared with Monte Carlo
[Brief discussion of Monte Carlo runs to set up comparison]

In Fig. \ref{fig:sol_mc_residual}, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing.

>>>>

\begin{figure}
    \centering
    \includegraphics{pdf_xinit0.0.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 0.0$. In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.} 
    \label{fig:sol_mc_residual_0}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{pdf_xinit6.0.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 6.0$. In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.} 
    \label{fig:sol_mc_residual_6}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{pdf_xinit12.0.pdf}
    \caption{Analytic solution for the outgoing spectrum compared with Monte Carlo at a line center optical depth of $\tau_0 = 1 \times 10^7$. Photons are initialized with $\rm x = 12.0$. In the log-scale plot in the second panel, $|\rm H_{bc}|$ is shown instead of $\rm H_{bc}$.} 
    \label{fig:sol_mc_residual_12}
\end{figure}

For each numerical solution, the monochromatic source of photons was initialized with a different starting frequency to evaluate the analytic solutions' accuracy with variation of the parameter $\rm \sigma_s$. This is related to $\rm x_{init}$ by

\begin{equation} \label{sigma0_xinit}
    \sigma_0 = \frac{\beta}{a} \rm x_{init}^3
\end{equation}

Monte Carlo numerical simulations were performed with $\rm x_{init} = (0.0, 2.0, 4.0 ... 12.0)$ and optical depths $\tau_0 = (10^6, 10^7)$. In Fig. \ref{fig:sol_mc_residual_0}, \ref{fig:sol_mc_residual_6} and \ref{fig:sol_mc_residual_12}, these are compared with the analytic solutions at selected initial frequencies. In each of these figures, the contribution of the flux from Eq. \ref{eq:Hbc} is examined alongside the solutions $H_{\rm d}$ and $H_{\rm 0}$. The corrected solution, $H_{\rm 0 + bc} = H_{\rm 0} + H_{\rm bc}$, has considerably lower residuals to Monte Carlo than the other solutions, especially in the line wing. It is evident that the solution $H_{\rm d}$ derived by \citet{1973MNRAS.162...43H} diverges significantly from the Monte Carlo simulations in the line wings. The $H_{\rm bc}$ correction term, when added to the solution $H_0$ derived by \citet{2006ApJ...649...14D}, produces a successful analytical result that characterizes the probability distribution of frequencies for escaping photons, including situations in which the photons are given initial frequencies outside of the line core.

This can best be seen by comparing the results shown in Fig. \ref{fig:sol_mc_residual_0} with those in Fig. \ref{fig:sol_mc_residual_12}. The $\rm H_{0+bc}$ analytic solution remains accurate in the line wing when photons are emitted away from line center, while the residuals of $\rm H_d$ and $\rm H_0$ become noticeably larger. It can be concluded that the $\rm H_{bc}$ correction term more accurately represents the additional flux from photons that escape without ever being scattered through the line core.
